Distance Sampling in \proglang{R}

### 2015-12-07 paper.Rmd
fig 4 caption

```{r minke-amakihi-hn-plot, echo=FALSE, warning=FALSE, fig.width=9, fig.height=4, fig.cap="Left: fitted detection functions overlayed on the histogram of observed distances for the minke whale data using half-normal model. Centre, right: plots of the probability density function for the amakihi models. Centre, hazard-rate with observer as a covariate; right, hazard-rate model with observer and minutes after sunrise as covariates. Points indicate probability of detection for a given observation (given that observations covariate values) and lines indicate the average detection function.\\label{fig:minkeamakihi}"}
par(mfrow=c(1, 3))
plot(minke_hn, showpoints=FALSE)
plot(amakihi_hr_obs, pdf=TRUE, cex=0.7)
plot(amakihi_hr_obs_mas, pdf=TRUE, cex=0.7)
```

>>>>

```{r minke-amakihi-hn-plot, echo=FALSE, warning=FALSE, fig.width=9, fig.height=4, fig.cap="Left: fitted detection function overlayed on the histogram of observed distances for the minke whale data using half-normal model. Centre, right: plots of the probability density function for the amakihi models. Centre, hazard-rate with observer as a covariate; right, hazard-rate model with observer and minutes after sunrise as covariates. Points indicate probability of detection for a given observation (given that observations covariate values) and lines indicate the average detection function.\\label{fig:minkeamakihi}"}
par(mfrow=c(1, 3))
plot(minke_hn, showpoints=FALSE)
plot(amakihi_hr_obs, pdf=TRUE, cex=0.7)
plot(amakihi_hr_obs_mas, pdf=TRUE, cex=0.7)
```
